Machine Learning guided workflow for Ribosome Binding Site engineering

### 2021-06-07 paper/main.tex

\subsection{Performance of the recommendation algorithm}

The design recommendations were made using the Multi-armed Bandit algorithm.
In short, this algorithm is a stochastic method of probing of the experimental space. 
This algorithm aims at maximising the reward (output) from testing a limited number of instances from a big pool which cannot be wholly tested due to limited resources (time, computational power, capital). 
In our case we use the Upper Confidence Bound version of the algorithm, which focuses its recommendations on sequences that should give highest TIR based on the probabilities computed by the prediction algorithm (see Figure \ref{fig:batch rec}).\\

@@

Figure \ref{fig: Scatterplot} shows our algorithms performance in terms of predictions in each round. 
As expected, the predictions in Round 0 were poor due to use of approximated data. 
The predictions improved for the subsequent rounds, from R\textsuperscript{2} of 0.065 for round 0 to R\textsuperscript{2} of 0.27 for round 3.
Similarly, the Spearman correlation coefficient rose from 0.27 for Round 0 to 0.48 for Round 3.
One important point to note is that the predictions are also influenced by our recommendation choices. 
In each round, we select a number of data points for exploration, which means that these data points, when tested, have a high chance of having real mean different to what was predicted.
However, this is still very useful information for future predictions as it allows us to understand the underlying space better.

@@

>>>>

\subsection{DESIGN: Performance of the recommendation algorithm}
\label{sec:ucb-results}

\cheng{Write this section to describe Figure 2, in the order of the subfigures (can rearrange if needed). Again, feels like a method section.}
The design recommendations were made using the Multi-armed Bandit algorithm.
In short, this algorithm is a stochastic method of probing of the experimental space. 
This algorithm aims at maximising the reward (output) from testing a limited number of instances from a big pool which cannot be wholly tested due to limited resources (time, computational power, capital). 
In our case we use the Upper Confidence Bound version of the algorithm, which focuses its recommendations on sequences that should give highest TIR based on the probabilities computed by the prediction algorithm (see Figure \ref{fig:batch rec}).\\

@@

\cheng{Start this section with these results.}
Figure \ref{fig: Scatterplot} shows how our algorithm performed in terms of predictions in each round. 
As expected, the predictions in Round 0 were poor due to use of approximated data. 
The predictions improved for the subsequent rounds, from R\textsuperscript{2} of 0.065 for round 0 to R\textsuperscript{2} of 0.27 for round 3.
Similarly, the Spearman correlation coefficient rose from 0.27 for Round 0 to 0.48 for Round 3.
One important point to note is that the predictions are also influenced by our recommendation choices. 
In each round, we select a number of data points for exploration, which means that these data points, when tested, have a high chance of having real mean different to what was predicted.
However, this is still very useful information for future predictions as it allows us to understand the underlying space better.

@@

\cheng{Have a look at the paper I wrote with Mengyan, and summarise the first few opportunities and challenges there.}
There are still open questions that need to be addressed for applying machine learning in synthetic biology.
For example, how can we understand the language of RBS sequences better?
In other words, can we extract more biologically important information from the decisions made by our algorithms?
Another example would be - given a small amount of RBS sequences tested, how can machine learning algorithm provide more accurate predictions and uncertainty measurement? 
Next question would be - how generalizable is this method? Can it be succesfully used for design of bigger genetic parts, like promoters?
Finally, another question with high impact on the performance of the workflow is - how should we choose the parameters which controls the exploration-exploitation rate? \\
